### 2024-10-19 src/Submission.Rnw
Update

\HRule{} \\[0.4cm]
{\huge \bfseries Group Project - Proposal } \\ [0.4cm]
\HRule{} \\[1cm]

@@

\section*{Subject area}:

\section*{Data set}:

\section*{Topics covered}:

\subsubsection*{ -Topic 1- }

\subsubsection*{ -Topic 2- }

\subsubsection*{ -Topic 3- }

\subsubsection*{ -Topic 4- }

>>>>

\HRule{} \\[0.4cm]
{\huge \bfseries Group Project } \\ [0.4cm]
\HRule{} \\[1cm]

@@

<<eval=TRUE>>=
# Note I made the default improve value large so the error is visible,
# because the MLE converges very quickly
theta_nr <- newton_raphson_mle(x, improve = 1e-1)

cat(
    "Maximum likelihood estimate of theta via Newton-Raphson method\n", 
    "MLE: ", round(theta_nr, 6), "\n",
    "Error: ", round(abs(theta_hat - theta_nr), 8),
    sep = ""
)
@
